Automatic Matching of Bullet Lands

### 2016-10-11 imaging-paper.tex
Make sure to include RData

\begin{figure}[hbtp]
\begin{subfigure}[t]{\textwidth}\centering
\caption{Maximal number of CMS between unknown bullet C-3 and all of the other 118 considered (known) lands. For two lands the number of maximum CMS is high. }
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.5\textwidth]{figure/cms-1}

@@

\end{knitrout}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Top 2 match with C-3 based on CMS.}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=\textwidth]{figure/top2-1}

@@

\begin{figure}[hbtp]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\includegraphics[width=.65\textwidth]{figure/strange-res-1}

>>>>

\begin{figure}[hbtp]
\begin{subfigure}[t]{\textwidth}\centering
\caption{Maximal number of CMS between unknown bullet C-3 and all of the other 118 considered (known) lands. For two lands the number of maximum CMS is high. }
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\color{warningcolor}{\#\# Warning in readChar(con, 5L, useBytes = TRUE): cannot open compressed file 'data/data-25-25/unkn9.RData', probable reason 'No such file or directory'}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}\end{kframe}
\includegraphics[width=.5\textwidth]{figure/cms-1}

@@

\end{knitrout}
\end{subfigure}
\begin{subfigure}[b]{.49\textwidth}\centering
\caption{Top 2 match with C-3 based on CMS.}
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in reslist[[which(cmsdist == 14)]]: attempt to select less than one element in get1index}}\end{kframe}
\includegraphics[width=\textwidth]{figure/top2-1}

@@

\begin{figure}[hbtp]
  \centering
\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in readChar(con, 5L, useBytes = TRUE): cannot open the connection}}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in reslist[[106]]: subscript out of bounds}}\end{kframe}
\includegraphics[width=.65\textwidth]{figure/strange-res-1}
